%%
%% Copyright (c) 2018-2019 Weitian LI <wt@liwt.net>
%% CC BY 4.0 License
%%
%% Résumé
%% ------
%% A short document (1-2 pages) to sum up the job-related accomplishments
%% and experience.
%%
%% Checklist
%% ---------
%% * Contact Information
%% * Work History / Experience
%% * Education
%% * Skills
%% * Summary & Objective (optional)
%% * Hobbies & Interests (optional)
%%
%% Credits
%% -------
%% * CV vs. Resume: What is the Difference? When to Use Which?
%%   https://uptowork.com/blog/cv-vs-resume-difference
%% * How to Make a Resume: A Step-by-Step Guide (+30 Examples)
%%   https://uptowork.com/blog/how-to-make-a-resume
%% * Entry-Level Resume: Sample and Complete Guide (+20 Examples)
%%   https://uptowork.com/blog/entry-level-resume-example
%%
%% Created: 2018-04-14
%%

% English version
\documentclass{resume}

% Adjust icon size (default: same size as the text)
\iconsize{\Large}

% File information shown at the footer of the last page
\fileinfo{%
  \faCopyright{} 2019, Kemiao HUANG \hspace{0.5em}
  \githublink{kemo-huang}{kemo-cv} \hspace{0.5em}
  \faEdit{} \today
}

\name{Kemiao}{Huang}

\keywords{BSD, Linux, Programming, Python, C, Shell, DevOps, SysAdmin}

% \tagline{\icon{\faBinoculars}} <position-to-look-for>}
% \tagline{<current-position>}

% \photo{<height>}{<filename>}

\profile{
  \mobile{189-2935-7397}
  \email{11610728@mail.sustech.edu.cn}
  \birthday{Nov. 1998} \\
  \home{Shenzhen, Guangdong, China}
  \github{Kemo-Huang}
  % Custom information:
  % \icontext{<icon>}{<text>}
  % \iconlink{<icon>}{<link>}{<text>}
}

\begin{document}
\makeheader

%======================================================================
% Summary & Objectives
%======================================================================
Within three years experience in Computer Science.

%======================================================================
\sectionTitle{Education}{\faGraduationCap}
%======================================================================
\begin{educations}
  \education%
    {September 2016}%
    [Present]%
    {Southern University of Science and Technology (SUSTech)}%
    {Department of Computer Science and Engineering}%
    {Computer Science}%
    {Bachelor}

%  \separator{0.5ex}
%  \education%
%    {September 2009}%
%    [June 2013]%
%    {Shanghai Jiao Tong University}%
%    {Department of Physics and Astronomy}%
%    {Applied Physics}%
%    {Bachelor's Degree}
\end{educations}

%======================================================================
\sectionTitle{Research of Interest}{\faStar}
%======================================================================
\begin{itemize}
  \item \textbf{Machine Learning}\\
  	asdsadas
  \item Use Ansible to manage a VPS running DragonFly BSD that serves
    personal email, authoritative DNS, website, Git, IRC, etc.
  \item Built and administrate the workstations, a 4-node computer cluster,
    and network facilities for the team.
  \item Participated in building and testing the SKA high-performance
    cluster prototype (1 login node + 1 data node + 4 computing nodes)
    in Shanghai Astronomical Observatory.
  \item Designed and developed the whole website (Django, Bootstrap, jQuery)
    for \enquote{The 1st China--New Zealand Joint SKA Summer School}
    in 2014.
    
\end{itemize}

%======================================================================
\sectionTitle{Experience}{\faAtom}
%======================================================================
\begin{itemize}
  \item Developed the low-frequency radio sky image simulation software:
    \link{https://github.com/liweitianux/fg21sim}{\texttt{FG21sim}}.
  \item Developed a suite of utilities to semi-automate the
    X-ray astronomical data analysis:
    \link{https://github.com/liweitianux/chandra-acis-analysis}{\texttt{chandra-acis-analysis}}.
  \item Separated the faint cosmological EoR signal along the frequency
    dimension using a Convolutional Denoising Autoencoder (CDAE).
  \item Classified the radio galaxies in the FIRST survey according to
    morphologies using a Convolutional Neutral Network (CNN).
  \item Significantly improved the modeling of radio halos,
    and integrated the instrumental effects of radio interferometers
    into the simulation pipeline.
  \item Improved the background modeling in X-ray spectral fitting
    achieved more accurate and robust fitting results.
  \item Published 2 first-author and 8 co-authored SCI papers.
\end{itemize}

%======================================================================
\sectionTitle{Projects}{\faCode}
%======================================================================
\begin{itemize}
  \item 
  \item \link{https://github.com/liweitianux/dfly-update}{\texttt{dfly-update}}:
    (Shell)
    A simple tool to update a DragonFly BSD system.
  \item \link{https://github.com/liweitianux/openrcs}{\texttt{openrcs}}:
    (C)
    Enhance \texttt{OpenBSD RCS}, to make it compatible with \texttt{GNU RCS}.
  \item \link{https://github.com/liweitianux/fg21sim}{\texttt{fg21sim}}:
    (Python)
    Simulate the low-frequency radio sky maps.
  \item \link{https://github.com/Kemo-Huang/}{\texttt{cdae-eor}}:
    (Python, Keras)
    Use a Convolutional Denoising Autoencoder (CDAE) to separate the
    faint EoR signal.
  \item \link{https://github.com/Kemo-Huang/autoware-exp}{\texttt{autoware-exp}}:
    (Robotic Operating System (ROS))
    2D / 3D object detections in Autoware for autonomous driving.
  \item \link{https://github.com/liweitianux/resume}{\texttt{resume}}:
    (\LaTeX)
    The template and source files of \emph{this} resume.
\end{itemize}

%======================================================================
\sectionTitle{Internships}{\faBriefcase}
%======================================================================
\begin{experiences}
  \experience%
    [July 2019]%
    {September 2019}%
    {Software Developer @ Shenzhen Haylion Technologies Co., Ltd.}%
    [\begin{itemize}
      \item Developed 
      \item Deployed the Airflow server and database to periodically
        retrieve product sales and advertising data from Amazon.
      \item Developed the website (Flask, jQuery) to help customers to
        optimize their advertising campaigns on Amazon.
    \end{itemize}]

%  \separator{0.5ex}
\end{experiences}

%======================================================================
\sectionTitle{Skills}{\faCogs}
%======================================================================
\begin{competences}[10em]
  \comptence{Operating Systems}{
    Linux, ROS
  }
  \comptence{Computer Vision}{%
    OpenCV, Pytorch, PCL
  }
  \comptence{Data Analysis}{%
    Scikit-learn, Pandas, MATLAB
  }
  \comptence{Development}{%
    Android, SpringBoot, Unity, Flask, WeChat mini-app
  }
\end{competences}

\end{document}
